# Reproducible Research: Peer Assessment 1

---
author: "B. Spangehl"
date: "Saturday, July 19, 2014"
output: html_document
---

```{r, echo=FALSE,results="hide"}
require(ggplot2)
```


### Loading and preprocessing the data
```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
fileZip <- "./activity.zip"

if (file.exists(fileZip) == F) {
  download.file(fileUrl, fileZip, mode = "wb")
  dateDownLoaded <- date()
}

df <- read.csv(unz(fileZip,"activity.csv")                
               ,colClasses=c("integer","Date","integer"),na.strings="NA")
```


### What is mean total number of steps taken per day?
```{r}
steps.date <- aggregate(list(steps=df$steps),list(date=df$date),sum)
```

1. Make a histogram of the total number of steps taken each day
```{r}
ggplot(steps.date, aes(x=steps)) + xlab("No. of Steps") + ylab("Count") + 
      geom_histogram(binwidth = 1000)
```

2. Calculate and report the **mean** and **median** total number of steps taken per day  
Mean of total number of steps taken per day: `r mean(steps.date$steps,na.rm=T)`.  
Median of total number of steps taken per day: `r median(steps.date$steps,na.rm=T)`.


### What is the average daily activity pattern?
1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


### Imputing missing values



### Are there differences in activity patterns between weekdays and weekends?
